Practical Effects of Integrating Temperature with Strang Split Reactions

### 2021-03-22 strang/paper.tex
new aastex
Fix affiliation
Non-parenthetical cite

\documentclass[times,preprint]{aastex63}

@@

\author[0000-0003-0439-4556]{M.~P.~Katz}
\affiliation{Nvidia Corp}

@@

Looking at global convergence of a reacting hydrodynamics problem we
see that second order convergence is only realized when temperature or
energy is evolved alongside the composition when using a Strang-split
approach to reactions.  This is just a single, rather simple problem,
but this suggests that reactive hydrodynamics simulations should
switch to integrating temperature or another energy equation together
with reactions to yield better overall convergence and accuracy.  This
complements the work of \citep{muller:1986} which showed that when
evolving near nuclear statistical equilibrium, evolving entropy
with the system is needed for stability.  We expect that for problems
with vigorous burning, such as detonations, directly coupling the composition
and thermodynamic evolution will be especially important.

\acknowledgements \castro\ is freely available at
\url{https://github.com/AMReX-Astro/Castro}.   The work at
Stony Brook was supported by DOE/Office of Nuclear Physics grant
DE-FG02-87ER40317.  This material is based upon work supported by the
U.S. Department of Energy, Office of Science, Office of Advanced
Scientific Computing Research and Office of Nuclear Physics,
Scientific Discovery through Advanced Computing (SciDAC) program under
Award Number DE-SC0017955.  This research was supported by the
Exascale Computing Project (17-SC-20-SC), a collaborative effort of
the U.S. Department of Energy Office of Science and the National
Nuclear Security Administration.

>>>>

\documentclass[times,preprint]{aastex631}

@@

\author[0000-0003-0439-4556]{M.~P.~Katz}
\affiliation{NVIDIA Corporation}

@@

Looking at global convergence of a reacting hydrodynamics problem we
see that second order convergence is only realized when temperature or
energy is evolved alongside the composition when using a Strang-split
approach to reactions.  This is just a single, rather simple problem,
but this suggests that reactive hydrodynamics simulations should
switch to integrating temperature or another energy equation together
with reactions to yield better overall convergence and accuracy.  This
complements the work of \cite{muller:1986} which showed that when
evolving near nuclear statistical equilibrium, evolving entropy
with the system is needed for stability.  We expect that for problems
with vigorous burning, such as detonations, directly coupling the composition
and thermodynamic evolution will be especially important.

\begin{acknowledgments}

\castro\ is freely available at
\url{https://github.com/AMReX-Astro/Castro}.   The work at
Stony Brook was supported by DOE/Office of Nuclear Physics grant
DE-FG02-87ER40317.  This material is based upon work supported by the
U.S. Department of Energy, Office of Science, Office of Advanced
Scientific Computing Research and Office of Nuclear Physics,
Scientific Discovery through Advanced Computing (SciDAC) program under
Award Number DE-SC0017955.  This research was supported by the
Exascale Computing Project (17-SC-20-SC), a collaborative effort of
the U.S. Department of Energy Office of Science and the National
Nuclear Security Administration.

\end{acknowledgments}
